### 2019-01-30 intro.tex
ssr

The following result points out that given a Boolean function $f$
in the form of a Boolean expression, it is \np-hard to approximate
the symmetry level to within any factor $\rho \geq 1$.

\begin{theorem}\label{thm:approx_sym_level_hard}
For any $\rho \geq 1$, it is \cnp-hard to approx
\end{theorem}

>>>>

\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The following result points out that given a Boolean function $f$
in the form of a Boolean expression, it is \cnp-hard to approximate
the symmetry level to within any factor $\rho \geq 1$.

\begin{theorem}\label{thm:approx_sym_level_hard}
For any $\rho \geq 1$, it is \cnp-hard to approx
\end{theorem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\fi

### 2019-01-30 preliminaries.tex
ssr

\subsection{Defintions: Symmetric Boolean Functions}
\label{sse:symmetry}

A pair of variables of a Boolean function $f(x_1, x_2, \ldots, x_n)$ is
said to be \textbf{symmetric} if their values can be interchanged without
affecting the value of the function.
This form of interchange symmetry partitions the set of variables into a set of
 \textbf{symmetry groups}, where the members of each group are pairwise symmetric.
Function $f$ is said to be
$r$-\textbf{symmetric} if it has at most $r$ symmetry groups.
In this case, the value of $f$
depends only on how many of the variables in each symmetry group have the value 1.
We say that $f$ is \textbf{properly} $r$-\textbf{symmetric} if
it is $r$-symmetric, but not $(r-1)$-symmetric.

In the literature, a 1-symmetric function $f$ is referred to simply
as a \textbf{symmetric} function.
Thus, if $f$ is a symmetric function, then for any
input $(a_1, a_2, \ldots, a_n)$ to $f$, where $a_i \in \{0,1\}$ for
$1 \leq i \leq n$, and any permutation $\pi$ of $\{1, 2, \ldots, n\}$,
$f(a_1, a_2, \ldots, a_n)$ = $f(a_{\pi(1)}, a_{\pi(2)}, \ldots, a_{\pi(n)})$.

>>>>

\subsection{Complexity of Estimating the Symmetry Level of a i
Boolean Function}
\label{sse:symmetry_level_hardness}

Recall that the symmetry level of a Boolean function $f$ is the smallest
integer $r$ such that the following condition holds:
the  inputs to $f$ can be partitioned into $r$ subsets 
(symmetry groups) so that the value of $f$ depends only on 
how many of the inputs in each group have the value 1.
The following result shows that given a Boolean function $f$
in the form of a Boolean expression, it is \cnp-hard to 
approximate\footnote{An algorithm approximates the symmetry
level of a Boolean function $f$ within the factor $\rho$ if it finds a
partition of the inputs to $f$ into at most $\rho \timex r^*$ symmetry
groups, where $r^*$ is the symmetry level of $f$.}
the symmetry level of $f$ to within any factor $\rho \geq 1$.

\newcommand{\cala}{\mbox{$\mathcal{A}$}}

\begin{proposition}\label{pro:approx_sym_level_hard}
For any $\rho \geq 1$, it is \cnp-hard to approximate the
symmetry level of $f$ to within the factor $\rho$.
\end{proposition}

\noindent
\textbf{Proof:}~ Suppose there is an efficient algorithm \cala{} 
that provides a $\rho$ approximation for the symmetry level
of a Boolean function for some $\rho \geq 1$.
We will show that \cala{} can be used to efficiently solve
the CNF Satisfiability problem (SAT) which is known 
to be \cnp-hard \cite{GJ-1979}.

Let $f$ be a CNF formula representing an instance of SAT.
Let $X$ = $\{x_1, x_2, \ldots, x_n\}$ denote the set of
Boolean variables used in $f$.

\QED

In contrast, we will show that the symmetry level of an NCF (or that of a
generalized NCF) can be computed efficiently.
